Corpus Creation

### 2020-08-22 inst/analysis/corpus-creation.Rmd
Updated corpus blacklisting ggm and shinyBS

---
title: "Corpus Creation"
output: 
  html_document: 
    theme: united
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: console
params:
  data_dir: /var/lib/R/project-evalR/revalstudy/data
  num_packages: 500
  output_dir: /var/lib/R/project-evalR/revalstudy/data
  which_dependencies:
    - Depends
    - Imports
---

@@

```{r get all available packages}
# TODO this should be installed.packages() once they are installed
cran_packages_raw <- available.packages()
cran_packages <- as_tibble(cran_packages_raw) %>%
  select(package=Package, version=Version)
```

@@

write_lines(pkgs_top_revdeps$package, CORPUS_FILE)
write_csv(pkgs_revdeps, CORPUS_REVDEPS)
write_lines(unique(pkgs_revdeps_raw$revdep), CORPUS_REVDEPS_FILE)
write_lines(unique(), CORPUS_ALL_PACKAGES_FILE)
```

>>>>

---
title: "Corpus Creation"
output: 
  html_document: 
    theme: united
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: console
params:
  base_dir: /home/rstudio/evalR
  hostname: prl2
  port: 8788
  num_packages: 500
  which_dependencies:
    - Depends
    - Imports
---

@@

```{r package blacklist}
blacklist <- tribble(
  ~package,
  "ggm",      # requires bioc
  "shinyBS"   # runs shiny server as part of its tests
)
```

```{r get all available packages}
# TODO this should be installed.packages() once they are installed
#cran_packages_raw <- available.packages()
cran_packages_raw <- installed.packages()
cran_packages <- as_tibble(cran_packages_raw) %>%
  select(package=Package, version=Version) %>%
  anti_join(blacklist, by="package")
```

@@

write_lines(sort(pkgs_top_revdeps$package), CORPUS_FILE)
write_csv(pkgs_revdeps, CORPUS_REVDEPS)
write_lines(sort(unique(pkgs_revdeps_raw$revdep)), CORPUS_REVDEPS_FILE)
```
